Design and Implementation of Probabilistic Programming Language Anglican

### 2016-11-20 paper/paper.tex
typo fixed and simpler language

The sole purpose of the algorithm identifier of \texttt{infer} is to invoke
an appropriate overloading or implementation of the function --- conventionally, 
the identifier is a keyword related to the
algorithm name (\texttt{:lmh} for Lightweight
Metropolis-Hasting, \texttt{:pcascade} for Particle Cascade
etc.). The second parameter is a query as defined by
the \texttt{defquery} form or its anonymous version \texttt{query}. For instance,
the following Clojure code invokes \texttt{infer} on an Anglican query
defined anonymously via the \texttt{query} form:
%If needed, the query
%can be defined anonymously, right in the argument list of a call
%to \texttt{infer}:
\begin{lstlisting}[style=default]
(let [x 1]
  (infer :pgibbs (query (predict x)) nil))
\end{lstlisting}
A query is executed by calling the initial continuation of the
query, which accepts a value and a state. The state is supplied
by the inference algorithm, while the value is provided as a
parameter of \texttt{infer}. A query does not have to have any
parameters, in which case the value can be simply \texttt{nil}.
When a query is defined with a binding for the initial value,
the value becomes available inside the query. A query may
accept multiple parameters using Clojure's structured binding.
For instance, it may take multiple parameters as components 
of an input vector. In this case, the initial value is given
as a structured value, such as a vector, and the components
of this value gets pattern matched to the corresponding
parameters of the query via the destructuring mechanism of Clojure.
%The value is destructured via pattern match in case of a structured binding. 
For example,
\begin{lstlisting}[style=default]
(defquery my-query [mean sd]
  (predict (sample (normal mean sd))))

>>>>

The sole purpose of the algorithm identifier of \texttt{infer} is to invoke
an appropriate overloading or implementation of the function --- conventionally, 
the identifier is a keyword related to the
algorithm name (\texttt{:lmh} for Lightweight
Metropolis-Hasting, \texttt{:pcascade} for Particle Cascade
etc.). The second parameter is a query as defined by
the \texttt{defquery} form or its anonymous version \texttt{query}. For instance,
the following Clojure code invokes \texttt{infer} on an Anglican query
defined anonymously via the \texttt{query} form:
%If needed, the query
%can be defined anonymously, right in the argument list of a call
%to \texttt{infer}:
\begin{lstlisting}[style=default]
(let [x 1]
  (infer :pgibbs (query (predict x)) nil))
\end{lstlisting}
A query is executed by calling the initial continuation of the
query, which accepts a value and a state. The state is supplied
by the inference algorithm, while the value is provided as a
parameter of \texttt{infer}. A query does not have to have any
parameters, in which case the value can be simply \texttt{nil}.
When a query is defined with a binding for the initial value,
the value becomes available inside the query. A query may
accept multiple parameters using Clojure's structured binding.
For instance, it may take multiple parameters as components 
of an input vector. In this case, the initial value is given
as a structured value, such as a vector, and the components
of this value are matched to the corresponding
parameters of the query via the destructuring mechanism of Clojure.
%The value is destructured via pattern match in case of a structured binding. 
For example,
\begin{lstlisting}[style=default]
(defquery my-query [mean sd]
  (predict (sample (normal mean sd))))
